taxize - taxonomic search and retrieval in R

### 2013-05-29 inst/doc/taxize_withcode.Rnw
started example - found bugs :(

>>>>

Suppose we have fuzzy coded trait table with 2 traits with 3 respectively 2 modalities:
<<>>=
(traits <- read.table(header = TRUE, sep = ';', text = 'taxon;T1M1;T1M2;T1M3;T2M1;T2M2
Gammarus sp.;0;0;3;1;3
Potamopyrgus antipodarum;1;0;3;1;3
Coenagrion sp.;3;0;1;3;1
Enallagma cyathigerum;0;3;1;0;3
Erythromma sp.;0;0;3;3;1
'))
@

And want to match this to a table with abundances:
<<>>=
(abundances <- read.table(header = TRUE, sep = ';', text = 'taxon;abundance
Gammarus roeseli;5
Gammarus roeseli;6
Gammarus tigrinus;7
Gammarus tigrinus;8
Coenagrionidae;10
Coenagrionidae;6
Potamopyrgus antipodarum;10
'))
@

classification(gsub(' sp.', '',traits$taxon), ID='tsn')

get_uid(gsub(' sp.', '',traits$taxon))

### 2013-05-29 inst/doc/taxize_withcode.tex
started example - found bugs :(

>>>>

Suppose we have fuzzy coded trait table with 2 traits with 3 respectively 2 modalities:
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
(traits <- \hlfunctioncall{read.table}(header = TRUE, text = \hlstring{"Family  Genus  Species\textbackslash{}tT1M1\textbackslash{}tT1M2\textbackslash{}tT1M3\textbackslash{}tT2M1\textbackslash{}tT2M2\textbackslash{}nGAMMARIDAE\textbackslash{}tGammarus\textbackslash{}tsp.\textbackslash{}t0\textbackslash{}t0\textbackslash{}t3\textbackslash{}t1\textbackslash{}t3\textbackslash{}nHYDROBIIDAE\textbackslash{}tPotamopyrgus\textbackslash{}tantipodarum\textbackslash{}t1\textbackslash{}t0\textbackslash{}t3\textbackslash{}t1\textbackslash{}t3\textbackslash{}nCOENAGRIONIDAE\textbackslash{}tCoenagrion\textbackslash{}tsp.\textbackslash{}t3\textbackslash{}t0\textbackslash{}t1\textbackslash{}t3\textbackslash{}t1\textbackslash{}nCOENAGRIONIDAE\textbackslash{}tEnallagma\textbackslash{}tcyathigerum\textbackslash{}t0\textbackslash{}t3\textbackslash{}t1\textbackslash{}t0\textbackslash{}t3\textbackslash{}nCOENAGRIONIDAE\textbackslash{}tErythromma\textbackslash{}tsp.\textbackslash{}t0\textbackslash{}t0\textbackslash{}t3\textbackslash{}t3\textbackslash{}t1\textbackslash{}n"}))
\end{alltt}
\begin{verbatim}
          Family        Genus     Species T1M1 T1M2 T1M3 T2M1 T2M2
1     GAMMARIDAE     Gammarus         sp.    0    0    3    1    3
2    HYDROBIIDAE Potamopyrgus antipodarum    1    0    3    1    3
3 COENAGRIONIDAE   Coenagrion         sp.    3    0    1    3    1
4 COENAGRIONIDAE    Enallagma cyathigerum    0    3    1    0    3
5 COENAGRIONIDAE   Erythromma         sp.    0    0    3    3    1
\end{verbatim}
\end{kframe}
\end{knitrout}

And want to match this to a table with abundances:
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
abundances <- \hlfunctioncall{read.table}(header = TRUE, sep = \hlstring{";"}, text = \hlstring{"taxon;abundance\textbackslash{}nGammarus roeseli;5\textbackslash{}nGammarus roeseli;6\textbackslash{}nGammarus tigrinus;7\textbackslash{}nGammarus tigrinus;8\textbackslash{}nCoenagrionidae;10\textbackslash{}nCoenagrionidae;6\textbackslash{}nPotamopyrgus antipodarum;10\textbackslash{}n"})
\end{alltt}
\end{kframe}
\end{knitrout}
